Interpretable Machine Learning

### 2017-12-04 talk.Rmd
add references

## Step 2: Throw ML on your data
```{r learn, warning=FALSE}
library('mlr')
set.seed(42)
task = makeRegrTask(data = survey.dat, target = 'CompensationAmount')
lrn = makeLearner('regr.randomForest', importance=TRUE)
mod = train(lrn, task)
```
## Step 3: Profit. We are done! {.center}

@@

@@

@@

@@

## 
```{r, echo=FALSE, fig.align='center'}
set.seed(44)
```
```{r, echo=TRUE, fig.align='center'}
dat = getTaskData(task)
explanation <- lime(dat, mod)
# Explain new instance
explainer <- lime::explain(dat[3, ], explanation, n_features = 3)
plot_features(explainer, ncol=1)
```

>>>>

## Step 2: Throw ML on your data
```{r learn, warning=FALSE}
library('mlr')
set.seed(42)
task = makeRegrTask(data = survey.dat, target = 'CompensationAmount')
lrn = makeLearner('regr.randomForest', importance=TRUE)
mod = train(lrn, task)
```
## Step 3: Profit. {.center}

@@

<font size="2">Goldstein, A., Kapelner, A., Bleich, J., & Pitkin, E. (2013). Peeking Inside the Black Box: Visualizing Statistical Learning with Plots of Individual Conditional Expectation, 1–22. https://doi.org/10.1080/10618600.2014.907095 </font>

@@

<font size="2">Friedman, J. H. (1999). Greedy Function Approximation : A Gradient Boosting Machine. North, 1(3), 1–10. https://doi.org/10.2307/2699986 </font>

@@

<font size="2">Breiman, Leo. "Random forests." Machine learning 45.1 (2001): 5-32. </font>

@@

## 
```{r, echo=FALSE, fig.align='center'}
set.seed(44)
dat = getTaskData(task)
```
```{r, echo=TRUE, fig.align='center'}
explanation <- lime(dat, mod)
explainer <- lime::explain(dat[3, ], explanation, n_features = 3)
plot_features(explainer, ncol=1)
```

<font size="2">Ribeiro, M. T., Singh, S., & Guestrin, C. (2016). “Why Should I Trust You?”: Explaining the Predictions of Any Classifier. Retrieved from http://arxiv.org/abs/1602.04938</font>
